---
title: "HW10"
output:
  html_document: default
  pdf_document: default
name: "Osuke Sashida"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r 1}
library(alr4)
library(carData)
data(Moore)
head(Moore)
attach(Moore)
as.factor(partner.status)
as.factor(fcategory)
```
(1)
Some predictor's P-value is not significant, which means this model has redundant predictor.
```{r 1-1}
Moore_model = lm(conformity~partner.status+fcategory+partner.status:fcategory)
summary(Moore_model)
```
(2)
"anova" tests using TypeI while "Anova" test using TypeII.
TypeII test doesn't care about interaction term.
We can see fcategory should be dropped.
```{r 1-2}
anova(Moore_model)
Anova(Moore_model, type="II")
```
(3)Those p-values are not significant. So this tells us those mean fcategory dont't work well.
```{r 1-3}
tmp <- aov(conformity~partner.status*fcategory,data=Moore)
TukeyHSD(tmp,which="fcategory")
```


## Problem2
(1)
We can say most of predictors has collinearity to another predictor.
```{r 2}
head(Rpdata)
attach(Rpdata)
plot(Rpdata)
```

(2)
All of predictors are significant in spite of having collinearity.
```{r 2-2}
rp_model = lm(y~x1+x2+x3+x4+x5+x6)
summary(rp_model)
```
(3)
Apprently this looks strange.
```{r 2-3}
residualPlot(rp_model)
```

## Problem3
(1)
This linear model looks fitted well and summary also shows.
```{r 3}
head(pipeline)
attach(pipeline)
pipe_model = lm(Lab~Field)
summary(pipe_model)
plot(Lab~Field)
abline(pipe_model)
```

(2)
We can tell there are outliers and variance tends to be bigger from residual versus fitted plot.
ncvTest tells us we should reject null hypothesis which means variance is not constant.
```{r 3-2}
residualPlot(pipe_model)
ncvTest(pipe_model)
```

## Problem4
(1)
Each variable and overall Tukey test aren't significant which means this model contains curvature but it can fit enough.
```{r}
head(water)
attach(water)
water_reg = lm(log(BSAAM)~log(APMAM)+log(APSAB)+log(APSLAKE)+log(OPBPC)+log(OPRC)+log(OPSLAKE))
summary(water_reg)
residualPlots(water_reg)
```

## Problem5
$E=(y_i-\hat{y}_{i(i)}|X)=\delta$

$H_0:\delta=0, H_a:\delta\not=0$

No.3 and 4 datas can reject null hypothesis which means these are outlier.
```{r}
n = 54
p = 5
std = 4
error = c(1,1.732,9,10.295)
hat_diag = c(0.9,0.75,0.25,0.185)
standard_resid = error/(std*sqrt(1-hat_diag))
student_resid = standard_resid*sqrt((n-p-1)/(n-p-(standard_resid)^2))
dffits = (1/p)*(standard_resid)^2*(hat_diag/(1-hat_diag))
df = data.frame(error, hat_diag, standard_resid, student_resid, dffits)
df
2*pt(standard_resid, n-p-1, lower.tail = FALSE)
```