---
title: "HW9"
output:
  html_document: default
  pdf_document: default
name: Osuke Sashida
---


```{r setup}
library(alr4)
```

## Problem1
These two models are not nested model. 
So we can't compare these model using F-test.
```{r 1}
head(UN11)
attach(UN11)
model1 = lm(lifeExpF~group)
model2 = lm(lifeExpF~log(ppgdp))
```

## Problem2
From summary P-value is lower than significane level. So we can reject null hypothesis which has just intercept.
```{r 2}
head(fuel2001)
attach(fuel2001)
alt_model= lm(FuelC~Tax+Drivers+Income+log(Miles))
summary(alt_model)
```

## Problem3
Alternative model is significant compare to each null model.
```{r 3}
head(cakes)
attach(cakes)
model_a = lm(Y~X1+I(X1^2)+X2+I(X2^2)+I(X1*X2))
summary(model_a)
model_n1 = lm(Y~X1+I(X1^2)+X2+I(X2^2))
anova(model_n1, model_a)
model_n2 = lm(Y~X1+X2+I(X2^2)+I(X1*X2))
anova(model_n2, model_a)
model_n3 = lm(Y~X2+I(X2^2))
anova(model_n3, model_a)
```
# Manual
```{r manual}
RSS_n1 = sum(resid(model_n1)^2)
RSS_a = sum(resid(model_a)^2)
df_n1 = 9
df_a = 8
f1 = ((RSS_n1-RSS_a)/(df_n1-df_a))/(RSS_a/df_a)
p_val1 = pf(f1,1,8, lower.tail = FALSE)
p_val1
```

## Problem4
$NH:b_2=0, AH:b_2\not=0$

P_value is 0.08085 so that we can't reject null hypothesis.
Which means $b_2=0$ has probability 0.0404 to be above or below 1.751 each. 
```{r 4}
head(Rateprof)
attach(Rateprof)
gender = as.factor(gender)
pepper = as.factor(pepper)
discipline = as.factor(discipline)
prof_model = lm(quality~gender+numYears+pepper+discipline+easiness+raterInterest)
summary(prof_model)
```
$NH:b_2=0, AH:b_2<0$

P_value is 0.9595852 so that we can't reject null hypothesis again.

$NH:b_2=0, AH:b_2>0$

P_value is 0.04041476 so that we can reject null hypothesis.
```{r 4-2}
pt(1.751, 347, lower.tail = TRUE)
pt(1.751, 347, lower.tail = FALSE)
Anova(prof_model, type = "II")
prof_model2 = lm(quality~numYears+pepper+discipline+easiness+raterInterest)
Anova(prof_model, type = "II")
prof_model3 = lm(quality~pepper+discipline+easiness+raterInterest)
Anova(prof_model, type = "II")
summary(prof_model3)
```

## Problem5
```{r 5}
head(twins)
attach(twins)
C = as.factor(C)
plot(IQb, IQf,pch = 19,col=C)
legend("topleft",
       legend = levels(C),
       pch = 19,
       col = factor(levels(C)))
twins_model = lm(IQf~IQb+C+IQb:C)
summary(twins_model)
Anova(twins_model, type="II")
twins_model2 = lm(IQf~IQb+C)
Anova(twins_model2, type="II")
twins_model3 = lm(IQf~IQb)
Anova(twins_model3, type="II")
summary(twins_model3)
```
