---
title: "HW11"
output:
  pdf_document: default
  html_document: default
name: Osuke Sashida
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
```

## Problem1
(a) This is non-constant variance and this even looks like $1/x$ curve.
```{r 1-a}
str(BigMac2003)
attach(BigMac2003)
plot(BigMac~FoodIndex)
```

(b) According to Tukey test this model can't reject null hypothesis, which means there isn't curavature.
```{r 1-b}
mac.reg = lm(BigMac~log(FoodIndex))
summary(mac.reg)
residualPlots(mac.reg)
```

(c) But residual variance is non-constant. Because p-value is significance so that this model will reject null hypothesis.
$NH: V(Y|X=x)=\sigma^2$

$AH: V(Y|X=x)=\sigma^2exp(\lambda x)$.
```{r 1-c}
ncvTest(mac.reg)
```

(d) Box-Cox procedure describes it is reasonalble to transform y to somewhere between one power of -0.6 and one power -0.08. So we can choose $1/\sqrt y$ in this case.
```{r 1-d}
summary(powerTransform(mac.reg))
```

(e) Apparently this model doesn't have non constant variance any more.
```{r 1-e}
remac.reg = lm((1/sqrt(BigMac))~log(FoodIndex))
summary(remac.reg)
ncvTest(remac.reg)

```

(f) Obviously 41th data point is outlier.
```{r 1-f}
outlierTest(remac.reg)
```

(g) We can tell 41 th data is outlier from this plot. Cook distance and studentize error are so high.
```{r 1-g}
BigMac2003[41,]
influenceIndexPlot(remac.reg)
```

(h)No outlier is in new dataset.
```{r 1-h}
newBigMac<-BigMac2003[-41,]
attach(newBigMac)
newmac.reg = lm((1/sqrt(BigMac))~log(FoodIndex))
summary(newmac.reg)
outlierTest(newmac.reg)
ncvTest(newmac.reg)
residualPlots(newmac.reg)
```

(i) As we can see, the slope and intercept don't look these have changed much. We can tell from actual values. Since that outlier's hat-value is not large. But each significance and overall significance are highly improved.
```{r 1-}
attach(BigMac2003)
plot((1/sqrt(BigMac))~log(FoodIndex))
abline(remac.reg)
summary(remac.reg)
attach(newBigMac)
plot((1/sqrt(BigMac))~log(FoodIndex))
abline(newmac.reg)
summary(newmac.reg)
```

## Problem2
As a result, 50th data plot is outlier and 50th data is Palm Beach.

After removing Palm Beach from dataset, DADE got to be outlier.

From Box-Cox Buchanan should be transformed to log then Palm Beach is no longer outlier.
```{r 2}
str(florida)
attach(florida)
plot(Buchanan~Bush)
text(Bush[50], Buchanan[50]-100,  labels="Palm Beach")
text(Bush[13], Buchanan[13]-100,  labels="DADE")
vote.reg = lm(Buchanan~Bush)
summary(vote.reg)
outlierTest(vote.reg)
florida[50,]

florida2 = florida[-50,]
attach(florida2)
vote2.reg = lm(Buchanan~Bush)
outlierTest(vote2.reg)
florida[13,]

attach(florida)
fix = powerTransform(vote.reg)
summary(fix)
fixvote.reg = lm(log(Buchanan)~Bush)
outlierTest(fixvote.reg)
plot(log(Buchanan)~Bush)
text(log(Bush[50]), Buchanan[50]-100,  labels="Palm Beach")
text(log(Bush[13]), Buchanan[13]-100,  labels="DADE")
abline(fixvote.reg)
```

## Problem3 
(1) Obviously we can tell this model is needed to transform from Tukey test.
```{r 3-1}
str(baeskel)
attach(baeskel)
plot(Tension~Sulfur)
sul.reg = lm(Tension~Sulfur)
residualPlots(sul.reg)
```

(2) $\lambda = 0$ model is the most likely to fit.
```{r 3-2}
x <- rep(1:12)
transformedx <- 1/x
transneg.reg = lm(Tension~transformedx)
plot(Tension~Sulfur)
abline(transneg.reg)

trans0.reg = lm(Tension~1)
plot(Tension~(1/Sulfur))
abline(trans0.reg)

plot(Tension~Sulfur)
abline(sul.reg)
```

(3) 
From Box-Cox we can conclude we don't have to trasform this model anymore.
```{r 3-3}
logsul.reg = lm(Tension~log(Sulfur))
summary(logsul.reg)
y_hat = predict(logsul.reg)
plot(y_hat~Tension)

bc = powerTransform(logsul.reg)
summary(bc)
```



## Problem4
Transformations of x for {-1,0,1} are not enough.
As we can see, quadratic polynomial regression has over 0.9 R squared value.
We can say it fits well and yet, Speed term is not significant.
```{r 4}
str(stopping)
attach(stopping)
stop.reg = lm(Distance~Speed)
plot(Distance~Speed)
abline(stop.reg)
bc = powerTransform(stop.reg)
summary(bc)

stop2.reg = lm(sqrt(Distance)~Speed)
plot(sqrt(Distance)~Speed)
abline(stop2.reg)
summary(stop2.reg)

x <- rep(1:62)
transformedx <- 1/x
stop_lam1.reg = lm(Distance~transformedx)
summary(stop_lam1.reg)
stop_lam2.reg = lm(Distance~1)
summary(stop_lam2.reg)
stop_lam3.reg = lm(Distance~Speed)
summary(stop_lam3.reg)

quad.reg = lm(Distance~Speed+I(Speed^2))
summary(quad.reg)
```