---
title: "HW 12 Last HW"
author: "Ronald Barry"
date: "4/16/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(leaps)
```

#### First HW Problem

Text problem 7.7

This experimental bias leads to 0 slope and making intercept close to average size of seeds.
Error doesn't change much.
```{r 1-1}
str(galtonpeas)
attach(galtonpeas)
plot(Progeny~Parent)

model = lm(Progeny~Parent)
summary(model)
weight <- 1 / lm(abs(model$residuals) ~ model$fitted.values)$fitted.values^2
wls = lm(Progeny~Parent, weights = weight)
summary(wls)
abline(wls)
detach(galtonpeas)
```

#### Second HW Problem

Text problem 10.3 (see notes below)

Forward selection chose $y=X_3$ while backward selection chose $y=X_1+X_2$.
However as we can see, $y=X_1+X_2$ is way better than $y=X_3$.
$y=X_3$ is not even like the second.
This is because if we consider just one parameter, $X_3$ is better than $X_1$, $X_2$.
That's why badly forward selection chose $X_3$.
This is like local optimization.

```{r 2}
str(mantel)
attach(mantel)
null.reg = lm(Y~1)
step(null.reg, scope=~X1+X2+X3, direction = "forward")

full.reg = lm(Y~X1+X2+X3)
step(full.reg, scope=~1, direction = "backward")

X = cbind(X1, X2, X3)
output = leaps(x=X, y=Y)
AIC_values <- rep(NA, 7)
for(i in 1:7){
the_model <- output$which[i,]
reg <- lm(Y ~ X[,the_model]) # each model tried
AIC_values[i] <- AIC(reg)
}
cbind(output$which, AIC_values)
detach(mantel)
```

#### Third HW Problem

Text problem 10.6 (see notes below)

$Y = NS/ES = Diversity$

Eventually, I selected $Y=log(Areaa)+Anear+Dist$

Obviously area of island is related to diversity.
The bigger island has more different environment, or opportunity for creatures to live there.
And also area of closest island is important.
Because for example birds can move their habit on to close island.
Also distance has the same reason.
```{r 3}
str(galapagos)
attach(galapagos)

Y=NS/ES
gal.reg = lm(Y~Area+Anear+Dist+DistSC)
residualPlots(gal.reg)

DistSC = DistSC+0.2
trans_gal.reg = lm(Y~log(Area)+Anear+Dist+DistSC)
residualPlots(trans_gal.reg)

step(trans_gal.reg, scope=~1, direction = "backward")
```

#### Fourth HW Problem

You can try a relatively simple logistic regression.

```{r }
library(car)
grain_size <- 
c(0.245, 0.247, 0.285, 0.299, 0.327, 0.347, 0.356, 0.36, 0.363, 
0.364, 0.398, 0.4, 0.409, 0.421, 0.432, 0.473, 0.509, 0.529, 
0.561, 0.569, 0.594, 0.638, 0.656, 0.816, 0.853, 0.938, 1.036, 
1.045)
spider <-
c("absent", "absent", "present", "present", "present", "present", "absent", "present", "absent", "present", "absent", "present", 
"absent", "present", "absent", "present", "present", "present", 
"absent", "absent", "present", "present", "present", "present", 
"present", "present", "present", "present")
spider <- recode(spider, "'absent'=0; 'present'=1")
reg1 <- glm(spider~grain_size, family=binomial)
summary(reg1)
reg0 <- glm(spider~1, family=binomial)
summary(reg0)
```

a) When do you use a logistic model?  How does it differ from regression?

For classification problem.
This estimates the probability of which group the data likely to be.


b) What is a **link** function?

It makes range between negative infinity to positive infinity respond to probability of 0 to 1.


c)  Plot the presence/absence variable **spider** against the predictor **grain_size**.  What do you see?

It looks like we have to use logistic regression.
Cause linear regression doesn't seem to work at all.


d) Examine the AIC values from the two models.  What model is best?  What is your conclusion?  (If you look really carefully, you'll notice that something slightly odd happened.)

Logistic regression model doesn't fit enough to tell difference between those two groups.
We need more absent data probably.
```{r 4-d}
extractAIC(reg0)
extractAIC(reg1)
plot(spider~grain_size)
xseq = seq(min(grain_size), max(grain_size), length=1000)
probs = predict(reg1, newdata=data.frame(x1=xseq), type="response")
lines(grain_size, probs)
```


NOTE:  Data from (2006) Suzuki, S., N. Tsurusaki, and Y. Kodama. *Distribution of an endangered burrowing spider Lycosa ishikariana in the San\'in Coast of Honshu, Japan (Araneae: Lycosidae)*. **Acta Arachnologica** 55: 79-86.

They measured grain size on 28 beaches and whether or not the spider was present.



==================================================

#### **COMMENTS**

NOTES:

Problem 10.3 comments: Code for the stepwise algorithm is below. Comment on the strange result for the Backward algorithm (hint: plot $Y$ vs $X1 + X2$). To get **AIC** and **BIC** for all $2^3 = 8$ models, use the **extractAIC()** function as shown in lecture notes and lab.

Code for Forward and Backward Stepwise Algorithms:

```{r, eval=FALSE}
library(alr4)
data(mantel)
reg.full <- lm(Y ~ X1 + X2 + X3, data=mantel)
reg.start <- lm(Y ~ 1, data=mantel)

step(reg.start, scope =~ X1 + X2 + X3, direction="forward")
step(reg.full, scope =~ 1, direction="backward")
```

Problem 10.6: For this problem,

1. Use the response $Y=NS/ES$, the ratio of number of  species to number of endemic species 

2. Fit the model with $Y$ and all regressors except elevation. That is $NS/ES = Area+Anear+Dist+DistSC4$. Construct and interpret residual plots and test for non-constant variance.

3. Show that the model using log-transformations of the above regressors satisfies linearity and constant variance assumptions. The variable DistSC contains a zero value. Add the constant 0.2 to this regressor before transforming.

4. Select a best model using the Backward stepwise algorithm.

5. Summarize your results. Decide on a final model. Report your estimated equation and discuss the relationships among the regressors in your model and the response. What do you learn about species diversity (actually the response $Y=NS/ES$)?

